SPARQL on the Open, Decentralised Web

### 2016-12-09 dissertation/acknowledgments.tex

I have made many friends in the community, for which I am thankful. Of
these, the following in no particular order have in one way or the
other shaped this work through personal contact beyond published
papers: Olaf Görlitz, Norman Gray, Ansgar Scherp, Frank Van Harmelen,
Olaf Hartig, Javier David Fernández García, Aidan Hogan, Maribel
Acosta and Philip Stutz.

>>>>

I have made many friends in the community, for which I am thankful. Of
these, the following in no particular order have in one way or the
other shaped this work through personal contact beyond published
papers: Olaf Görlitz, Norman Gray, Ansgar Scherp, Frank Van Harmelen,
Olaf Hartig, Javier David Fernández García, Aidan Hogan, Maribel
Acosta, Josef Noll and Philip Stutz.

### 2016-12-09 dissertation/introdefhistory.tex

As noted in Section~\ref{sec:contribsum}, the scope of the study is
very broad, ranging from the practical programming details to
philosophy of science. With a scope of this breadth, the investigation
is shallow, it is hoped that some key insights will provoke further
investigation rather than being the end of any conversations. 
The overarching problem this work tries to address is this:

\begin{framed}
\begin{quote}
To achieve a Semantic Web where anyone can say anything about
anything, and where everyone is enabled to analyse data that have been
contributed, there is a difficult balance between centralising
infrastructure and decentralising it, and between processing on
clients and servers.
\end{quote}
\end{framed}

>>>>

As noted in Section~\ref{sec:contribsum}, the scope of the study is
very broad, ranging from the practical programming details to
philosophy of science. With a scope of this breadth, the investigation
is shallow, it is hoped that some key insights will provoke further
investigation rather than being the end of any conversations.

### 2016-12-09 dissertation/introduction.tex

The triple pattern is also a fundamental building block of the SPARQL
query language, which is the language that is the main topic of this
dissertation. SPARQL is an extensive, standardised query language with
both read and write operations. The syntax is near Turtle, but as the
above triple patterns, introduces variables. A set of triple patterns
may be used to create a conjunctive query, and along with a filter
that can be used to further constrain the query with boolean
expressions. Together, they are known as a Basic Graph Pattern
(BGP). More advanced parts of the language are built around BGPs.

@@

It is difficult to many developers to interact with RDF, and
contributions to alleviate that are summarised in
Section~\ref{sec:schm}.

>>>>

The triple pattern is also a fundamental building block of the SPARQL
query language, which is the language that is the main topic of this
dissertation. SPARQL is an extensive, standardised query language with
both read and write operations. The syntax is near Turtle but as the
above triple pattern shows, introduces variables. A set of triple patterns
may be used to create a conjunctive query, and along with a filter
that can be used to further constrain the query with boolean
expressions. Together, they are known as a Basic Graph Pattern
(BGP). More advanced parts of the language are built around BGPs.

@@

Many developers find it difficult to interact with RDF, and
contributions to alleviate that are summarised in
Section~\ref{sec:schm}.
